---
title: "Letter Sent"
date: Nov 26, 2019
author: Andriy Koval
output:
  html_document:
    df_print: kable
    theme: simplex
    toc: yes
    toc_float: yes
    code_folding: show
---
This report investigates the relationship between whether a follow up communication was sent (`letter_sent`) and various predictors in the study. 

<!-- These two chunks should be added in the beginning of every .Rmd that you want to source an .R script -->
<!--  The 1st mandatory chunck  -->
<!--  Set the working directory to the repository's base directory -->
```{r, echo=F, message=F} 
#Don't combine this call with any other chunk 
# cat("Working directory: ", getwd()) # check where you are
  library(knitr)
# Rmd is in "./reports/reportA/reportA.Rmd", but now the root is "./"
  knitr::opts_knit$set(root.dir='../../') 
```

<!--  The 2nd mandatory chunck  -->
<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# set options shared by all chunks
opts_chunk$set(
  results='show', 
  message = TRUE,
  comment = NA, 
  tidy = FALSE,
  fig.height = 4, 
  fig.width = 5.5, 
  out.width = "550px",
  fig.path = 'figure_rmd/',     
  dev = "png",
  dpi = 400
  # fig.path = 'figure_pdf/',     
  # dev = "pdf"#,
  # dev.args=list(pdf = list(colormodel = 'cmyk'))
)
echoChunks <- TRUE
cacheChunks <- TRUE
options(width=120) #So the output is 50% wider than the default.
# connect to the file with the underlying R script  
read_chunk("./analysis/logistic/model-1.R") 
```
This documents narrates the examination of the no-show data from pediatric urology clinic. 

# Environment
Packages that will be used in this analysis: 
<!-- Load 'sourced' R files.  Suppress the output when loading packages. --> 
```{r load-packages, echo=TRUE, message=FALSE, warning=FALSE}
```


<!-- Load the sources.  Suppress the output when loading sources. --> 
```{r load-sources, echo=echoChunks, message=FALSE}
```


<!-- Load any Global functions and variables declared in the R file.  Suppress the output. --> 
```{r declare-globals, echo=echoChunks, results='show', message=FALSE}
```

<!-- Declare any global functions specific to a Rmd output.  Suppress the output. --> 
```{r, echo=echoChunks, message=FALSE}
#Put code in here.  It doesn't call a chunk in the codebehind file.
```

# Data

Import the data prepared by the `./manipulation/0-greeter.R` 
<!-- Load the datasets.   -->
```{r load-data, echo=echoChunks, results='show', message=FALSE}
```

To better understand the data set, let us inspect quantitative properties of each variable
<!-- Inspect the datasets.   -->
```{r inspect-data, echo=echoChunks, results='show', message=FALSE}
```

<!-- Tweak the dataset   -->
```{r tweak-data, echo=TRUE, results='show', message=FALSE}
```

```{r drop-small-groups, echo=TRUE, results='show', message=FALSE}
```

# Model
```{r model-function, echo=echoChunks, results='show', message=FALSE,warning=F,cache=cacheChunks}
```

## Model 01 - Letter Sent
```{r m01, echo=echoChunks, results='show', message=FALSE,warning=F,cache=cacheChunks}
```

Observations:  
- `provider` was significantly  MD and PA were significantly more likely to send the letter after the visit:
# Sex of the patient was signifantly related to recieving the letter



## 1 - Reason for visit
```{r letter_1, echo=echoChunks, fig.height=8, fig.width=12, message=FALSE, warning=FALSE, cache=cacheChunks, results='show', out.width="1200"}
```







session information
===========================================================================

For the sake of documentation and reproducibility, the current report was rendered in the following environment.  Click the line below to expand.

<details>
  <summary>Environment <span class="glyphicon glyphicon-plus-sign"></span></summary>
```{r session-info, echo=FALSE}
if( requireNamespace("devtools", quietly = TRUE) ) {
  devtools::session_info()
} else {
  sessionInfo()
} 
```
</details>

```{r session-duration, echo=FALSE}
```



