---
title: "Returned to Care"
date: Nov 26, 2019
author: Andriy Koval
output:
  html_document:
    df_print: kable
    theme: simplex
    toc: yes
    toc_float: yes
    code_folding: show
---
This report investigates the relationship between whether the patient retured to care (`returned_to_care`) and various predictors in the study

<!-- These two chunks should be added in the beginning of every .Rmd that you want to source an .R script -->
<!--  The 1st mandatory chunck  -->
<!--  Set the working directory to the repository's base directory -->
```{r, echo=F, message=F} 
#Don't combine this call with any other chunk 
# cat("Working directory: ", getwd()) # check where you are
  library(knitr)
# Rmd is in "./reports/reportA/reportA.Rmd", but now the root is "./"
  knitr::opts_knit$set(root.dir='../../') 
```

<!--  The 2nd mandatory chunck  -->
<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# set options shared by all chunks
opts_chunk$set(
  results='show', 
  message = TRUE,
  comment = NA, 
  tidy = FALSE,
  fig.height = 4, 
  fig.width = 5.5, 
  out.width = "900px",
  fig.path = 'figure_rmd/',     
  dev = "png",
  dpi = 400
  # fig.path = 'figure_pdf/',     
  # dev = "pdf"#,
  # dev.args=list(pdf = list(colormodel = 'cmyk'))
)
echoChunks <- TRUE
cacheChunks <- TRUE
options(width=120) #So the output is 50% wider than the default.
# connect to the file with the underlying R script  
read_chunk("./analysis/logistic/model-1.R") 
```
# Environment
Packages that will be used in this analysis: 
<!-- Load 'sourced' R files.  Suppress the output when loading packages. --> 
```{r load-packages, echo=TRUE, message=FALSE, warning=FALSE}
```


<!-- Load the sources.  Suppress the output when loading sources. --> 
```{r load-sources, echo=echoChunks, message=FALSE}
```


<!-- Load any Global functions and variables declared in the R file.  Suppress the output. --> 
```{r declare-globals, echo=echoChunks, results='show', message=FALSE}
```

<!-- Declare any global functions specific to a Rmd output.  Suppress the output. --> 
```{r, echo=echoChunks, message=FALSE}
#Put code in here.  It doesn't call a chunk in the codebehind file.
```

# Data

Import the data prepared by the `./manipulation/0-greeter.R` 
<!-- Load the datasets.   -->
```{r load-data, echo=echoChunks, results='show', message=FALSE}
```

To better understand the data set, let us inspect quantitative properties of each variable
<!-- Inspect the datasets.   -->
```{r inspect-data, echo=echoChunks, results='show', message=FALSE}
```

<!-- Tweak the dataset   -->
```{r tweak-data, echo=TRUE, results='show', message=FALSE}
```

```{r drop-small-groups, echo=TRUE, results='show', message=FALSE}
```

# Questions 

1. Does sending a letter increase likelihood of return to care?  

2. What factors increase probability of return to care if we exclude predictors that are not significant? The predictors we are the most interested in are: reason for visit, insurance type, provider, and prior no show. 

3. Does provider (MD vs ARNP vs PA) predict return to care when looking at reason for visit and if they've had a prior no show?

4. Does insurance type predict return to care? What if compared with reason for visit as well?

5. What populations do MD vs ARNP vs PA see based on reason for visit ? There is a bias in this - ARNP is more likely to see voiding and PA is more likely to see penile. 

# Model

```{r model-function, echo=echoChunks, results='show', message=FALSE,warning=F,cache=cacheChunks}
```

## All predictors
```{r m00, echo=echoChunks, results='show', message=FALSE,warning=F,cache=cacheChunks}
```

## Selected predictors
```{r m00a, echo=echoChunks, results='show', message=FALSE,warning=F,cache=cacheChunks}
```

## Selected combinations
```{r m00b, echo=echoChunks, results='show', message=FALSE,warning=F,cache=cacheChunks}
```

<!-- ### Graph 00  -->
<!-- ```{r graph-00, echo=echoChunks, fig.height=8, fig.width=12, message=FALSE, warning=FALSE, cache=cacheChunks, results='show', out.width="1200"} -->
<!-- ``` -->

## Letter Sent
```{r returned_0, echo=echoChunks, results='show', message=FALSE,warning=F,cache=cacheChunks,fig.height=8, fig.width=12}
```

## Insurance
```{r returned_1, echo=echoChunks, results='show', message=FALSE,warning=F,cache=cacheChunks,fig.height=8, fig.width=12}
```

## PM Appointment
```{r returned_2, echo=echoChunks, results='show', message=FALSE,warning=F,cache=cacheChunks,fig.height=8, fig.width=12}
```

## Preferred Language
```{r returned_3, echo=echoChunks, results='show', message=FALSE,warning=F,cache=cacheChunks,fig.height=8, fig.width=12}
```

## Gender
```{r returned_4, echo=echoChunks, results='show', message=FALSE,warning=F,cache=cacheChunks,fig.height=8, fig.width=12}
```

## History of No-Show
```{r returned_5, echo=echoChunks, results='show', message=FALSE,warning=F,cache=cacheChunks,fig.height=8, fig.width=12}
```

## Month of Appointment
```{r returned_6, echo=echoChunks, results='show', message=FALSE,warning=F,cache=cacheChunks,fig.height=8, fig.width=12}
```

## Provider
```{r returned_7, echo=echoChunks, results='show', message=FALSE,warning=F,cache=cacheChunks,fig.height=8, fig.width=12}
```
## Reason for Visit
```{r returned_8, echo=echoChunks, results='show', message=FALSE,warning=F,cache=cacheChunks,fig.height=8, fig.width=12}
```


session information
===========================================================================

For the sake of documentation and reproducibility, the current report was rendered in the following environment.  Click the line below to expand.

<details>
  <summary>Environment <span class="glyphicon glyphicon-plus-sign"></span></summary>
```{r session-info, echo=FALSE}
if( requireNamespace("devtools", quietly = TRUE) ) {
  devtools::session_info()
} else {
  sessionInfo()
} 
```
</details>

```{r session-duration, echo=FALSE}
```



